fGFPCA dynamic prediction (In-sample)

### 2022-12-01 f-GFPCA.Rmd
more edits to progress report

### Local GLMMS

@@

Now let's try to predict future outcomes based on observations $\boldsymbol{Y}$ up to $t_m$.

@@

$$\hat{\boldsymbol{\xi}} = E(\boldsymbol{\xi}|\boldsymbol{Y}) =  \boldsymbol{\hat{\Gamma}\Phi ^T}(\boldsymbol{\Phi\hat{\Gamma}\Phi^T}+\hat{\sigma_{\epsilon}}^2\boldsymbol{I_m})^{-1}(\hat{\boldsymbol{\eta}}-\hat{\boldsymbol{f}}_0)$$
Where:

- $\hat{\boldsymbol{\Gamma}}$ is the diagonal covariance matrix of eigenvalues
- $\boldsymbol{\Phi}$ is the matrix of eigenfunctions up to $t_m$. These should be constant across all subjects.
- $\hat{\sigma_{\epsilon}}^2$ is the residual variance from FPCA
- $\hat{\boldsymbol{\eta}}$ is the estimated latent Gaussian function up to $t_m$
- $\hat{\boldsymbol{f}}_0$ is the FPCA mean function up to $t_m$

>>>>

### Local GLMMs

@@

Now let's try to predict future outcomes based on observations $\boldsymbol{Y}_m$ up to $t_m$.

@@

$$\hat{\boldsymbol{\xi}} = E(\boldsymbol{\xi}|\boldsymbol{Y}_m) =  \boldsymbol{\hat{\Gamma}\Phi ^T_m}(\boldsymbol{\Phi_m\hat{\Gamma}\Phi^T_m}+\hat{\sigma_{\epsilon}}^2\boldsymbol{I_m})^{-1}(\hat{\boldsymbol{\eta}}_m-\hat{\boldsymbol{f}}_0^m)$$
Where:

- $\hat{\boldsymbol{\Gamma}}$ is the diagonal covariance matrix of eigenvalues
- $\boldsymbol{\Phi}_m$ is the matrix of eigenfunctions up to $t_m$. These should be constant across all subjects.
- $\hat{\sigma_{\epsilon}}^2$ is the residual variance from FPCA
- $\hat{\boldsymbol{\eta}}_m$ is the estimated latent Gaussian function up to $t_m$
- $\hat{\boldsymbol{f}}_0^m$ is the FPCA mean function up to $t_m$

And then, we use the FPCA model for point prediction on the entire binned grid:

$$\hat{\boldsymbol{\eta}} = \hat{\boldsymbol{f}}_0+\boldsymbol{\Phi}\hat{\boldsymbol{\xi}}$$

Here, $\boldsymbol{\Phi}$ is the eigenfunctions on the entire binned grid. For $\hat{\boldsymbol{\eta}}$, even though it is calculated for the entire binned grid, we will take values after $t_m$.
